Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-23 documents/mixtures/mixture_models.tex
todo done
don't use the word sampling

Whenever an investigator is fitting PSF-convolved exponential or
de~Vaucouleurs profiles, the models presented here will improve code
performance.  That doesn't mean that doing such fitting is a Good
Idea.  These profiles are effective models for galaxies at low
signal-to-noise (as they are used in the \project{SDSS}) and they are
useful templates for performing consistent photometry across
morphologically diverse objects (as we use them in \citealt{bundy}).
They are sometimes used to distinguish disk and bulge light; these
uses are very prone to over-interpretation: There is no theoretical
argument and only weak observational arguments that the
rotation-supported parts of galaxies are always exponential and that
the kinematically hot components are de~Vaucouleurs.

>>>>

Whenever an investigator is fitting PSF-convolved exponential or
de~Vaucouleurs profiles, the models presented here will improve code
performance.  That doesn't mean that doing such fitting is a Good
Idea.  These profiles are effective models for galaxies at low
signal-to-noise (as they are used in the \project{SDSS}) and they are
useful templates for performing consistent photometry across
morphologically diverse objects (as we use them in \citealt{bundy}).
More radically, these profiles are sometimes used to distinguish disk
and bulge light; these uses are very prone to over-interpretation:
There is no theoretical argument and only weak observational arguments
that the rotation-supported parts of galaxies are always exponential
and that the kinematically hot components are always more
de-Vaucouleurs-like.
